Astro 507; Problem Set 3

### 2022-02-24 pset3/solutions.tex
3e

\documentclass[12pt, letterpaper, twoside]{article}
\usepackage{nopageno,epsfig, amsmath, amssymb}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}

@@

>>>>

\documentclass[12pt, letterpaper, twoside]{article}
\usepackage{nopageno,epsfig, amsmath, amssymb}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
}
\usepackage{empheq}

@@

\question{3e. \textbf{Polytropes}}
\answer{
    We are given the two following equations
    \begin{align}
        \rho_c &= 8.44 \unit{g}{cm^{-3}} \frac{M}{R^3} \\
        R M^{1/3} &= \frac{0.13}{(\mu_e F_{1/2}(z))^{2/3}}
    \end{align}
    First, let's quickly find the mass per electron in units of the proton mass, $\mu_e$, knowing that the gas is 90\% hydrogen (1 nucleon, 1 electron) and 10\% helium (4 nucleons, 2 electrons).
    \begin{equation}
        \mu_e = 0.9 \cdot 1 + 0.1 \cdot 2 = 1.1
    \end{equation}
    Now we can combine these equations to instead write that
    \begin{align}
        M &= \frac{\rho_c R^3}{8.44 \unit{g}{cm^{-3}}} \\
        R &= \qty[\frac{0.13}{(\mu_e F_{1/2}(z))^{2/3}} \qty(\frac{\rho_c}{8.44 \unit{g}{cm^{-3}}})^{-1/3}]^{1/2}
    \end{align}
    Plugging in our numbers $\mu_e = 1.1$, $z = 1.65$ and $\rho_c = 325 \unit{g}{cm^{-3}}$ to get R (and then M) gives
    \begin{empheq}[box=\fbox]{align}
        R &= 0.15 \unit{R_{\odot}} \\
        M &= 0.13 \unit{M_{\odot}}
    \end{empheq}
}
